\section{Order Theory}

\begin{definition}[Preorder]
    Let $X$ be a set. A \emph{preorder} on $X$ is a binary relation $\leq$ on $X$ such that:
    \begin{description}
        \item[Reflexivity] For all $x \in X$, we have $x \leq x$
        \item[Transitivity] For all $x, y, z \in X$, if $x \leq y$ and $y \leq z$ then $x \leq z$.  
    \end{description}
\end{definition}

\begin{definition}[Preordered Set]
    A \emph{preordered set} consists of a set $X$ and a preorder $\leq$ on $X$.
\end{definition}

\begin{definition}[Interval]
    Let $X$ be a preordered set and $Y \subseteq X$. Then $Y$ is an \emph{interval} if and only if, for
    all $a, b \in Y$ and $c \in X$, if $a \leq c \leq b$ then $c \in Y$.
\end{definition}

\begin{definition}[Linear Continuum]
    A linearly ordered set $L$ is a \emph{linear continuum} if and only if:
    \begin{enumerate}
        \item every nonempty subset of $L$ that is bounded above has a supremum
        \item $L$ is dense
    \end{enumerate}
\end{definition}

\begin{proposition}
    Every interval in a linear continuum is a linear continuum.
\end{proposition}

\begin{proof}
    \pf
    \step{1}{\pflet{$L$ be a linear continuum and $I$ an interval in $L$.}}
    \step{2}{Every nonempty subset of $I$ that is bounded above has a supremum in $I$.}
    \begin{proof}
        \step{a}{\pflet{$X \subseteq I$ be nonempty and bounded above by $b \in I$.}}
        \step{b}{\pflet{$s$ be the supremum of $X$ in $L$.}}
        \begin{proof}
            \pf\ Since $L$ is a linear continuum.
        \end{proof}
        \step{c}{$s \in I$}
        \begin{proof}
            \step{i}{\pick\ $a \in X$}
            \begin{proof}
                \pf\ Since $X$ is nonempty (\stepref{a}).
            \end{proof}
            \step{ii}{$a \leq s \leq b$}
            \step{iii}{$s \in I$}
            \begin{proof}
                \pf\ Since $I$ is an interval (\stepref{1}).
            \end{proof}
        \end{proof}
        \step{d}{$s$ is the supremum of $X$ in $I$}
    \end{proof}
    \step{3}{$I$ is dense.}
    \begin{proof}
        \step{a}{\pflet{$x, y \in I$ with $x < y$}}
        \step{b}{\pick\ $z \in L$ with $x < z < y$}
        \begin{proof}
            \pf\ Since $L$ is dense.
        \end{proof}
        \step{c}{$z \in I$}
        \begin{proof}
            \pf\ Since $I$ is an interval.
        \end{proof}
    \end{proof}
    \qed
\end{proof}

\begin{definition}[Ordered Square]
    The \emph{ordered square} $I_o^2$ is the set $[0,1]^2$ under the dictionary order.
\end{definition}

\begin{proposition}
    The ordered square is a linear continuum.
\end{proposition}

\begin{proof}
    \pf
    \step{2}{Every nonempty subset of $I_o^2$ bounded above has a supremum.}
    \begin{proof}
        \step{a}{\pflet{$X \subseteq I_o^2$ be nonempty and bounded above by $(b,c)$}}
        \step{b}{\pflet{$s = \sup \pi_1(X)$}}
        \begin{proof}
            \pf\ The set $\pi_1(X)$ is nonempty and bounded above by $b$.
        \end{proof}
        \step{c}{\case{$s \in \pi_1(X)$}}
        \begin{proof}
            \step{i}{\pflet{$t = \sup \{ y \in [0,1] \mid (s,y) \in X \}$}}
            \begin{proof}
                \pf\ This set is nonempty and bounded above by $c$.
            \end{proof}
            \step{ii}{$(s,t)$ is the supremum of $X$.}
        \end{proof}
        \step{d}{\case{$s \notin \pi_1(X)$}}
        \begin{proof}
            \pf\ In this case $(s,0)$ is the supremum of $X$.
        \end{proof}
    \end{proof}
    \step{3}{$I_o^2$ is dense.}
    \begin{proof}
        \step{a}{\pflet{$(x_1,y_1),(x_2,y_2) \in I_o^2$ with $(x_1,y_1) < (x_2,y_2)$}}
        \step{b}{\case{$x_1 < x_2$}}
        \begin{proof}
            \step{i}{\pick\ $x_3$ with $x_1 < x_3 < x_2$}
            \step{ii}{$(x_1,y_1) < (x_3,y_1) < (x_2,y_2)$}
        \end{proof}
        \step{c}{\case{$x_1 = x_2$ and $y_1 < y_2$}}
        \begin{proof}
            \step{i}{\pick\ $y_3$ with $y_1 < y_3 < y_2$}
            \step{ii}{$(x_1,y_1) < (x_1,y_3) < (x_2,y_2)$}
        \end{proof}
    \end{proof}
    \qed
\end{proof}